
---
title: "Assignment1_Vamsi_Nalluri"
output:
  word_document: default
  html_document: default
---
```{r}
#Clear the Workspace
rm(list = ls())
```

## Install the required packages and libraries , as required,  at appropriate chunks.

***

```{r}
library(ISLR)
library(dplyr)
library(glmnet)
library(caret)
```

## Loading the  Data from ISLR library (Carseats)

***
```{r}
Carseats_Filtered <- Carseats %>% select("Sales", "Price", "Advertising","Population","Age","Income","Education")
```

***
## Seperating Sales(Dependent Variable) and Other Data (Independent Variables) 

***
## Converting the Data into Matrix form : A required step for Glmnet model to work

***
```{r}
Carseats_Sales <- Carseats_Filtered$Sales
Carseats_Other <- data.matrix(Carseats_Filtered[, c(-1)])
```


## Data Pre-Processing: Standardizing the data and displaying the Summary of the Data

***
```{r}
preProc <- preProcess(Carseats_Other, method=c("center", "scale"))
Carseats_Scaled <- predict(preProc,Carseats_Other)
summary(Carseats_Scaled)
```

# Build the Lasso Regression Model by default its Lasso Model (if aplha = 1 is not mentioned). By default k fold cross validation is k=10

***
```{r}

Model <- cv.glmnet(Carseats_Scaled,Carseats_Sales , alpha = 1)

Lambda_Best <- Model$lambda.min
Lambda_Best

#produce plot of test MSE by lambda value
plot(Model) 
```

***
1.Optimal Lambda value is 0.004305309

***

## Finding the Coefficients for the Best model with the Optimal Lambda

***

```{r}
Model_Best <- glmnet(Carseats_Scaled,Carseats_Sales, alpha = 1, lambda = Lambda_Best)
coef(Model_Best)
```

***
2.Coefficent of Price is -1.35384596

***
## Finding the remaining variables with lambda of 0.01 and 0.1

***

```{r}
Model_Best1 <- glmnet(Carseats_Scaled,Carseats_Sales, alpha = 1, lambda = 0.01)
coef(Model_Best1)
Model_Best2 <- glmnet(Carseats_Scaled,Carseats_Sales, alpha = 1, lambda = 0.1)
coef(Model_Best2)
```

***

3.With Lambda 0.01 all the variables are remaining But with 0.1 population & Education variables are going out.

  As lambda increases variables will drop.

***

## Best lambda for Elastic Model (alpha=0.6)

***

```{r}
Model1 <- cv.glmnet(Carseats_Scaled,Carseats_Sales , alpha = 0.6)

Lambda_Best1 <- Model1$lambda.min
Lambda_Best1

#produce plot of test MSE by lambda value
plot(Model1) 
```

***
4.Optimal Lambda for elastic model is 0.006538062
